Instructions for EMNLP 2016 Proceedings

### 2016-04-22 doc/header-emnlp.tex
adapted preambles to accommodate The One Paper

\title{Instructions for EMNLP 2016 Proceedings\Thanks{This
    document has been adapted from the instructions for earlier ACL
    and NAACL proceedings, including those for
    NAACL-HLT 2016 by Margaret Mitchell and Adam Lopez,
    NAACL HLT15 by Matt Post and Adam Lopez,
    NAACL HLT12 by Nizar Habash and William Schuler,
    NAACL HLT10 by Claudia Leacock and Richard Wicentowski,
    NAACL HLT09 by Joakim Nivre and Noah Smith, 
    for ACL05 by Hwee Tou Ng and Kemal Oflazer,
    for ACL02 by Eugene Charniak and Dekang Lin, and earlier ACL and
    EACL formats.  Those versions were written by several people,
    including John Chen, Henry S. Thompson and Donald Walker.
    Additional elements were taken from the formatting instructions of
    the {\em International Joint Conference on Artificial Intelligence}
    and the {\em Conference on Computer Vision and Pattern Recognition}.}}

@@

\begin{document}

\maketitle

>>>>

\title{Instructions for EMNLP 2016 Proceedings}

@@

%%%\begin{document}

%%%\maketitle
